---
title: "Yi Lui Data Analysis: Transfer Efficiency"
author: "MFK"
date: "25/08/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup}
pacman::p_load(dplyr,brms,tidyr,ggplot2,lme4,lubridate,ggpval)

```


# Fluorescent powder
This imports Yi lui's data and skim the columns using skimr

```{r Yi's data import}
dY<-vroom::vroom("../data/Yi.data.longformat.20191121_censoring_handled.csv") %>% janitor::clean_names()
dY
# convert to UK date
dy<-dY %>% mutate(date=lubridate::mdy(date))
skimr::skim(dY)
```
## Fix date

Some of the dates are in American format, some are in British format.

```{r}
dY <- dY %>% separate(date,into = c("a","b","year"),sep = "/") %>% 
            mutate(date=case_when(a =="07"~paste0(b,"/",a,"/",year),
                        a !="07"~paste0(a,"/",b,"/",year)),.keep="unused")
```


# Plot the individual intensity/powder area vs contact number for all the surfaces

We think the date has an important contribution to the levels of intensity because the batteries were changed at some point in the UV light.


```{r rel intensity vs contact number and by date}
dY %>% 
  filter(gloves=="N") %>% 
  #filter(surface=="Plastic" ) %>% 
  #filter(id<21) %>% 
  ggplot()+
  geom_point(aes(x=contact_number,y=raw_int_d/(powder_area),colour=date),alpha=0.1)+
  #geom_smooth(aes(x=contact_number,y=raw_int_d/(powder_area)),method="lm",se=FALSE)+
  scale_y_continuous(trans="log10",limits=c(3e4,4e5 ))+
  ylab("Intensity/Powder Area")+
  xlab("Contact number")+
  facet_wrap(~date)+
  # scale_colour_brewer(palette = "Set1")+
  theme_bw()+
  #labs(color = "Gloves")+
  #font_size(14)
  theme(text = element_text(size=14),
  axis.text.x=element_text(size=14),
  axis.text.y=element_text(size=14))

```

## Remove last four dates

```{r remove dates of bimodal data}
dY <- dY %>% 
  filter(date<"23/07/2019")
```


# Plot contacts of first 20

```{r individual plots}

# Individual powder area vs contact number and loading weight 
dY %>% 
  filter(surface=="Plastic" ) %>% 
  filter(id<21) %>% 
  ggplot()+
  geom_point(aes(x=contact_number,y=raw_int_d/(powder_area),colour=gloves),size=5)+
  #geom_smooth(aes(x=contact_number,y=raw_int_d/(powder_area),colour=gloves),method="lm",se=FALSE)+
  scale_y_continuous(trans="log10",limits=c(3e4,4e5 ))+
  ylab("Intensity/Powder Area")+
  xlab("Contact number")+
  facet_wrap(~id)+
  scale_colour_brewer(palette = "Set1")+
  theme_bw()+
  labs(color = "Gloves")+
  #font_size(14)
  theme(text = element_text(size=14),
  axis.text.x=element_text(size=14),
  axis.text.y=element_text(size=14))->a
a

  ggsave(a,filename = "images/individual_relative_int_vs_contact_number.png",dpi=300, device="png",width = 15, height = 10, units = "in",bg="white")



# Raw int violin plots faceted by surface
dY %>% 
  # filter(surface=="Plastic" ) %>% 
  # group_by(surface,contact_number,gloves) %>% 
  # summarise(Mean=mean(powder_area),SD=sd(powder_area))
  ggplot()+
  geom_violin(aes(x=as.factor(contact_number),y=raw_int_d,fill=gloves),draw_quantiles = c(0.25,0.5,0.95))+
  scale_y_continuous(trans = "log10")+
  scale_fill_brewer(palette = "Set1")+
  facet_wrap(~surface,scales="free",nrow=3)+
  ylab("Raw intensity")+
  xlab("Contact number")+
  labs(fill = "Gloves")+
  hrbrthemes::theme_ipsum()

```

# Some investigative plots

```{r investigative plots}
#Plot log10(raw_int_d) vs contact_number for each ID and colour by gloves
dY%>%
filter(surface=="Plastic") %>%
filter(id>20 & id<=40) %>%
ggplot()+
geom_point(aes(x=contact_number,y=raw_int_d,colour=gloves),size=4)+
scale_colour_brewer(palette="Set1")+
scale_y_continuous(trans="log10")+
facet_wrap(~id)+
xlab("Contact number")+
ylab("Intensity units")+
theme_bw()+
labs(color='Gloves')+
theme(text = element_text(size=14),axis.text.x=element_text(size=14))  ->a

#save ggplot figure
# ggsave(a,"images/intensity_for_each_ID.png",device="png",units=c("cm"),width=30)
ggsave(a,filename = "images/intensity_for_each_ID_plastic_21_40.png",dpi=300, device="png",width = 10, height = 10, units = "in")


# Create a scatter plot of the intensity for each ID and colour by gloves, facet by surface

dY%>%
ggplot()+
geom_jitter(aes(x=contact_number,y=raw_int_d/powder_area,colour=date),size=4,alpha=0.4)+
scale_colour_brewer(palette="Set1")+
# geom_smooth(method="lm",se=TRUE,aes(x=contact_number,y=raw_int_d/powder_area,colour=gloves))+
facet_grid(gloves~surface)+
xlab("Contact number")+
ylab("Intensity units")+
scale_y_continuous(trans = "log10")+
theme_bw()+
labs(color='Date')+
theme(text = element_text(size=14),axis.text.x=element_text(size=14))  ->a

ggsave(a,filename = "images/aggregated_intensity.png",dpi=300, device="png",width = 12, height = 10, units = "in")




```



## Violin plots

```{r investigative violin plots}

dY%>%
  mutate(experimentID=paste0(id,surface,gloves)) %>% 
  group_by(experimentID) %>% 
  mutate(rel_int_d=raw_int_d/first(raw_int_d)) %>% 
  mutate(gloves=case_when(gloves=="Y"~glove_size_group,
                          gloves=="N"~"None")) %>% 
  filter(!is.na(gloves)) %>% 
  # drop_na() %>% 
  mutate(gloves=factor(gloves,levels=c("None","Small","Medium","Large"))) %>% 
  ggplot()+
  geom_violin(aes(x=as.factor(contact_number),y=rel_int_d/loading_weight,fill=surface),draw_quantiles = c(0.25,0.5,.75))+
  geom_smooth(aes(x=contact_number,y=rel_int_d/loading_weight),color="black",method="lm")+
  scale_fill_brewer(palette="Set1")+
  # geom_smooth(method="lm",se=TRUE,aes(x=contact_number,y=raw_int_d/powder_area,colour=gloves))+
  facet_grid(surface~gloves)+
  xlab("Contact number")+
  ylab("Relative Intensity units / Loading Weight")+
  scale_y_continuous(trans = "log10",labels = scales::label_number())+
  theme_bw()+
  labs(color='Surface')+
  theme(text = element_text(size=14),axis.text.x=element_text(size=14)) 
```

# LMER4 model fit
Here we fit a Linear Mixed Effects Model using LMER4 to the data.

```{r LMER4 raw_int_d }
#Here we fit a LMER4 model from LMER4 to the data, with raw_ind_d as the dependent variable
#We
model_fit_g<-lme4::lmer(log10(raw_int_d)~powder_area + contact_number + gloves + surface + (powder_area+contact_number+gloves+surface | id),
                  data = dY,
                  weights=log10(raw_int_d))
summary(model_fit_g)
plot(model_fit_g)

```


## Violin plots of glove effect Y/N by surface 

```{r Only first contact - violin plots}

dY%>%
  mutate(experimentID=paste0(id,surface,gloves)) %>% 
  group_by(experimentID) %>% 
  mutate(rel_int_d=raw_int_d/first(raw_int_d)) %>% 
  # mutate(gloves=case_when(gloves=="Y"~glove_size_group,
  #                         gloves=="N"~"None")) %>% 
  filter(!is.na(gloves)) %>% 
  filter(contact_number=="1") %>% 
  # drop_na() %>% 
  # mutate(gloves=factor(gloves,levels=c("None","Small","Medium","Large"))) %>% 
  ggplot()+
  geom_violin(aes(x=as.factor(contact_number),y=raw_int_d/powder_area/loading_weight,fill=gloves),draw_quantiles = c(0.25,0.5,.75))+
  # geom_smooth(aes(x=contact_number,y=raw_int_d/loading_weight),color="black",method="lm")+
  scale_fill_brewer(palette="Set1")+
  # geom_smooth(method="lm",se=TRUE,aes(x=contact_number,y=raw_int_d/powder_area,colour=gloves))+
  facet_grid(~surface)+
  xlab("Contact number")+
  ylab("Raw Intensity units / Loading Weight")+
  scale_y_continuous(trans = "log10",labels = scales::label_number())+
  theme_bw()+
  labs(color='Surface')+
  theme(text = element_text(size=14),axis.text.x=element_text(size=14)) ->p

add_pval(ggplot_obj = p)

# Put p-value
```


## Gradient of concentration

Let's look at the gradient for each participant. We can normalise every raw intensity value by first contact.

```{r}

dY%>%
  mutate(experimentID=paste0(id,surface,gloves)) %>% 
  group_by(experimentID) %>% 
  mutate(rel_int_d=raw_int_d/first(raw_int_d)) %>% 
  ggplot()+
  geom_jitter(aes(x=contact_number,y=rel_int_d),size=1.2,alpha=0.1,width=0.05,height=0)+
  geom_smooth(aes(x=contact_number,y=rel_int_d,colour=surface),method="lm")+
  scale_colour_brewer(palette="Set1")+
  # geom_smooth(method="lm",se=TRUE,aes(x=contact_number,y=raw_int_d/powder_area,colour=gloves))+
  facet_grid(~gloves)+
  xlab("Contact number")+
  ylab("Intensity units")+
  scale_y_continuous(trans = "log10")+
  theme_bw()+
  labs(color='Surface')+
  theme(text = element_text(size=14),axis.text.x=element_text(size=14)) 

```
## Relative intensity By glove size

Same as above but by glove size (Small, medium and large, no gloves)

```{r rel intensity vs glove size}
dY%>%
  mutate(experimentID=paste0(id,surface,gloves)) %>% 
  group_by(experimentID) %>% 
  mutate(rel_int_d=raw_int_d/first(raw_int_d)) %>% 
  mutate(gloves=case_when(gloves=="Y"~glove_size_group,
                          gloves=="N"~"None")) %>% 
  filter(!is.na(gloves)) %>% 
  # drop_na() %>% 
  mutate(gloves=factor(gloves,levels=c("None","Small","Medium","Large"))) %>% 
  ggplot()+
  geom_jitter(aes(x=contact_number,y=rel_int_d/loading_weight),size=1.2,alpha=0.1,width=0.05,height=0)+
  geom_smooth(aes(x=contact_number,y=rel_int_d/loading_weight,colour=surface),method="lm")+
  scale_colour_brewer(palette="Set1")+
  # geom_smooth(method="lm",se=TRUE,aes(x=contact_number,y=raw_int_d/powder_area,colour=gloves))+
  facet_grid(~gloves)+
  xlab("Contact number")+
  ylab("Relative Intensity units / Loading Weight")+
  scale_y_continuous(trans = "log10")+
  theme_bw()+
  labs(color='Surface')+
  theme(text = element_text(size=14),axis.text.x=element_text(size=14)) 
```



# LMER4 model fit
Here we fit a Linear Mixed Effects Model using LMER4 to the data.

```{r LMER4 raw_int_d }
#Here we fit a LMER4 model from LMER4 to the data, with raw_ind_d as the dependent variable
#We
model_fit_g<-lme4::lmer(log10(raw_int_d)~powder_area + contact_number + gloves + surface + (powder_area+contact_number+gloves+surface | id),
                  data = dY,
                  weights=log10(raw_int_d))
summary(model_fit_g)
plot(model_fit_g)

```

# BRMS model fit
Here we fit a Bayesian Regression Model using BRMS to the data.

```{r BRM raw_int_d }
#Here we fit a BRM model from BRSM to the data, with raw_ind_d as the dependent variable
#We 
model_fit_BRMS<-brms::brm(data = dY,raw_int_d~powder_area+contact_number+gloves+surface+(powder_area+contact_number+gloves+surface|id),
                       family = lognormal(link = "identity", link_sigma = "log"))
summary(model_fit_BRMS)
plot(model_fit_BRMS)

model_fit_BRMS

```

## Calculate Lambda - Transfer efficiency 




